---
title: "Who does more pushups"
author: "Bill kitto"
date: "March 8"
output: pdf_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?


# Methods

We will look at a pair of boxplots that shows pushups for both skill and line players to see if there is any apparent differences.

<Perform a variable analysis, and based on that nalysis choose at least one apprpriate graphical method and one appropriate numerical method to address the research question.>

# Results

<You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.>

## Graphical Results
```{r}
bwplot(pushups~position,
       data=pushups,
 xlab="number of pushups",
 main="Comparing positions")
```




<Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.>

## Numerical Results

<Discuss only the features of your numericla output that are relvant to answerting the Research Question.  Mention these features explicitly in your discussion.>

# Discussion and Conclusion

<State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.>